---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Installation

You can install the most recent updates of scMD from github with:

```{r setup, eval = FALSE}
# install devtools if necessary
install.packages('devtools')

# install the scMD package
devtools::install_github('randel/scMD')

# load
library(scMD)
```

## Data

We've made available pre-processed scMD [signatures](https://github.com/randel/scMD/tree/main/Processed_data_450k850k) in CSV format for your convenience. You're welcome to download and use them directly.

If you have your own bulk data for brain tissues and want to apply scMD directly, follow the instructions below to estimate cell type proportions. Please be aware that our estimations focus on seven primary brain cell types: Astrocytes, Endothelial Cells, Excitatory Neurons, Inhibitory Neurons, Microglia, Oligodendrocytes, and OPC.

```{r, eval = FALSE}
# Estimate cell type proportions
Est.prop.scMD = scMD(bulk = test_bulk, bulk_type = test_bulk_type)
                               
# Estimate when you have your own scDNAm data
#Est.prop.scMD = scMD(bulk = test_bulk, bulk_type = NULL,dat = beta_mtx,DM_df = df)

```


